Metropolitan Statistical Area Evaluation

### 2022-11-13 src/demo_data_wrangling.Rmd
calculating portland ME employment data

MSA_emp_income <- income_potential_MSAs %>% 
  right_join(avg_emp_yoy) %>% 
  filter(year == "2021") %>% 
  select(!c(avg_employment_rate, year))

@@

```{r}
# adding portland employment rates from https://data.bls.gov/pdq/SurveyOutputServlet
portland_employment_data <- read_csv(here("data", "raw", "portland_me_employment.csv")) %>% 
  row_to_names(row_number = 10) %>% 
  clean_names() %>% 
  select(year, jan) %>% 
  rename(civilian_labor = jan)

>>>>

MSA_emp_income <- income_potential_MSAs %>% 
  full_join(avg_emp_yoy) %>% 
  filter(year == "2021") %>% 
  select(!c(avg_employment_rate, year))

@@

```{r}
# adding portland employment rates from https://data.bls.gov/pdq/SurveyOutputServlet
portland_employment_data <- unemployment_data %>% 
  filter(year >= 2019) %>% 
  filter(cbsa == "76750") %>% 
   group_by(year) %>% 
  summarize(avg_employment_rate = mean(employment_rate)) %>% 
  mutate(avg_emp_YoY = (avg_employment_rate-lag(avg_employment_rate))/lag(avg_employment_rate)*100) %>% 
  mutate(avg_emp_YoY = round(avg_emp_YoY, digits = 3))
